Tempo Analysis: The Sound of Teaching Music 1

### 2020-07-28 script/RNotebook/ioi.Rmd
update analysis with the latest trimmed
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

- Last checked: 07/02/20

@@

# Sequence plot
## Articulation{#sequence_art}
```{r seq_art, fig.width = 20, fig.height = 5, echo = FALSE}
# For each individual
ioi_art_seq <- aggregate(IOI~SubNr*Condition*Skill*Interval, data = df_ioi_art,
                                 FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
ioi_art_seq <- cbind(ioi_art_seq[,1:4], as.data.frame(ioi_art_seq[,5]))
# Change colnames
colnames(ioi_art_seq) <- c("SubNr", "Condition", "Skill", "Interval", "N", "Mean", "SD")

@@

## Dynamics{#sequence_dyn}
```{r seq_dyn, fig.width = 20, fig.height = 5, echo = FALSE}
# For each individual
ioi_dyn_seq <- aggregate(IOI~SubNr*Condition*Skill*Interval, data = df_ioi_dyn,
                                 FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
ioi_dyn_seq <- cbind(ioi_dyn_seq[,1:4], as.data.frame(ioi_dyn_seq[,5]))
# Change colnames
colnames(ioi_dyn_seq) <- c("SubNr", "Condition", "Skill", "Interval", "N", "Mean", "SD")

>>>>

- Last checked: `r format(Sys.Date(), "%d-%b-%Y")`

@@

# Sequence plot
## Articulation{#sequence_art}
```{r seq_art, fig.width = 20, fig.height = 4, echo = FALSE}
# For each individual
ioi_art_seq <- aggregate(IOI~SubNr*Condition*Skill*Interval, data = df_ioi_art,
                                 FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
ioi_art_seq <- cbind(ioi_art_seq[,1:4], as.data.frame(ioi_art_seq[,5]))
# Change colnames
colnames(ioi_art_seq) <- c("SubNr", "Condition", "Skill", "Interval", "N", "Mean", "SD")

@@

## Dynamics{#sequence_dyn}
```{r seq_dyn, fig.width = 20, fig.height = 4, echo = FALSE}
# For each individual
ioi_dyn_seq <- aggregate(IOI~SubNr*Condition*Skill*Interval, data = df_ioi_dyn,
                                 FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
ioi_dyn_seq <- cbind(ioi_dyn_seq[,1:4], as.data.frame(ioi_dyn_seq[,5]))
# Change colnames
colnames(ioi_dyn_seq) <- c("SubNr", "Condition", "Skill", "Interval", "N", "Mean", "SD")
